Inferring cosmology from gravitational waves using non-parametric detector-frame mass distribution

### 2024-08-13 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Inference of $H_0$}

@@

\subsection{Inference of $H_0$ and $\Lambda$}

@@

Following the same procedure as in the previous subsection, except that we use the \textsc{scipy} optimization algorithm mentioned in Sec.~\ref{sec:pe} in this example, we get the result of the \ac{PE} shown in Fig.~\todo{add figure}.

@@

\subsection{Future work}
\label{sec:future_work}
As mentioned in Sec.~\ref{sec:pe}, our method is not a Bayesian inference, as we only consider the optimization of the parameters.
To perform a full Bayesian inference, we need to develop a likelihood function that considers the comparison of the two populations.
With this likelihood, our method will give the same result as the standard hierarchical Bayesian inference, as long as the number of reconstructions is large enough.

@@

>>>>

\subsection{Inference of $H_0$}
\label{sec:inference_H0}

@@

\subsection{Inference of $H_0$ and $\Lambda$}
\label{sec:inference_multi}

@@

Following the same procedure as in the previous subsection, except that we use the \textsc{scipy} optimization algorithm mentioned in Sec.~\ref{sec:pe} in this example, we get the result of the \ac{PE} shown in Fig.~\todo{add figure}.
The result shows that our method can infer multiple parameters simultaneously.

In principle, more parameters can be inferred with our method, for example, the present mass density $\Omega_m$ in the $\Lambda$CDM model.
However, the optimization procedure becomes more computationally expensive as the number of parameters increases.

@@

\subsection{Prospective improvements}
\label{sec:prospective}
As mentioned in Sec.~\ref{sec:pe}, our method is not a Bayesian inference, as we only consider the optimization of the parameters.
To perform a full Bayesian inference, we need to develop a likelihood function that considers the comparison of the two populations.
With this likelihood, our method will give the same result as the standard hierarchical Bayesian inference, as long as the number of reconstructions is large enough.

@@

We also mentioned a limitation of the method in Sec.~\ref{sec:inference_multi}.
The runtime of the optimization procedure scales with the number of parameters.
To perform higher dimensional analysis, we need to study using, instead of $d_\mathrm{JS}$, other distance measures that allow for faster optimization.
Either a distance measure that gives a simpler geometry to be optimized or a distance measure that can be calculated faster will be useful.
Other optimization algorithms should also be considered to allow for higher dimensional analysis and faster runtime.
